Which fifteen-minutes neighborhoods are dead-ends? An analysis of the network attributes of fifteen-minute pedsheds

### 2024-10-18 paper/paper.Rmd
small edits in methodology

The method proposed involves to study 15-minute walking neighborhoods in two stages. The first stage comprises assessing accessibility levels from the normative perspective of the provision of opportunities. In the second stage, the results of this analysis are correlated to neighborhood network attributes, including connectivity, centrality, and clustering.

>>>>

The proposed method involves studying 15-minute walking neighborhoods in two stages. The first stage assesses accessibility levels from a normative perspective, focusing on the provision of opportunities. In the second stage, the results are correlated with neighborhood network attributes, including connectivity, centrality, and clustering.
